Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-04-20 ProbabilisticCoherence.tex
Probabilistic forecast reconcliation schematic plot included with explanation

>>>>

This definition extends the notion of forecast reconciliation to the probabilistic setting.   Under point reconciliation methods, the reconciled point forecast is equal to the unreconciled point forecast after the latter is passed through two linear mappings. Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear mappings.  This is depicted schematically in Figure~\ref{fig:pfr_sch}.

\begin{figure}
	\input{Figs/probforerec_schematic.tex}
	\caption{Summary of probabilistic forecast reconciliation.  The probability that ${\bm y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.  Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pfr_sch} 
\end{figure}
